Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-11-29 paper_comparison/paper_comparison/paper_comparison.Rmd
update power cmp

Figure \ref{fig:polypower} shows the estimated power of visual test on lineups produced by the non-linearity model with the $X_{raw}$ following a uniform distribution against the natural logarithm of the effect $log_e(E)$ with comparison to the power of an exact test - F-test, and two other residual-based conventional tests commonly used in regression diagnostics but for testing heteroskedasticity and non-normality respectively. At the bottom of the figure \ref{fig:polypower}, there are a sequence of example residuals plots with increasing levels of $log_e(E)$. Readers can evaluate them from left to right and determine at which level the departure from a good residual plot becomes detectable.

In overall, the power of all four tests increases as the effect gets larger. The power curve of F-test climbs aggressively from 25% to around 90% as $log_e(E)$ increases from 0 to 2, while power of other tests respond inactively to the change of effect and remain lower than 25% throughout the period, showing that F-test is way more sensitive to the type of model defects that being considered. Meanwhile, no noticeable visual features can be spotted from the example residuals plots.

The power of visual test arises steadily to around 90% as $log_e(E)$ increases from 2 to 5, suggesting that the effect starts to make significant impact on the degree of the presence of the designed visual features. This can also be observed from the example residuals plots that when $log_e(E) = 2.5$, a weak "S-shape" starts to present. And as $log_e(E)$ increases, the visual pattern becomes much clearer. Other two inappropriate conventional tests shows improvement at the same time but at a lower rate. This coincides the point made by @cook1982residuals that residual-based tests for a specific type of model defect are sensitive to other types of model defects.

At $log_e(E) \approx 6$, the power of both F-test and visual test reaches almost 100%. The power of Breusch--Pagan test and Shapiro--Wilk test reach around 75% and 30% respectively.

Similarly, Figure \ref{fig:heterpower} shows the power of BP test, visual test and two other

@@

set.seed(10085)
ex_dat <- heter_model(a = 1, x = rand_uniform(-1, 1), b = 1)$gen(n = 100)
plist <- list()
j <- 0

>>>>

Figure \ref{fig:polypower} show the estimated power of visual test on lineups produced by the non-linearity model with the $X_{raw}$ following a uniform distribution, against the natural logarithm of the effect $log_e(E)$ with comparison to the power of an exact test - F-test, and two other residual-based conventional tests commonly used in regression diagnostics but for testing heteroskedasticity and non-normality respectively. At the bottom of the figure \ref{fig:polypower}, there are a sequence of example residuals plots with increasing levels of $log_e(E)$. Readers can evaluate them from left to right and determine at which level the departure from a good residual plot becomes detectable.

Figure \ref{fig:heterpower} is similar to Figure \ref{fig:polypower}, but shows corresponding information on lineups produced by the heteroskedasticity model. In this scenario, the visual test is compared to an approximate test - Breusch-Pagan test, and two other inappropriate tests - F-test and Shapiro-Wilk test.

For the non-linearity model, the power of all four tests increases as the effect gets larger. The power curve of F-test climbs aggressively from 25% to around 90% as $log_e(E)$ increases from 0 to 2, while power of other tests respond inactively to the change of effect and remain lower than 25% throughout the period, showing that F-test is way more sensitive to the type of model defects that being considered. Meanwhile, no noticeable visual features can be spotted from the example residuals plots.

In terms of the heteroskedasticity model, the power of Breusch-Pagan test is also almost always greater than the power of visual test. For $0 \leq log_e(E) \leq 2$, where the visual feature is nearly unobservable from the example residual plots and the power curve of the visual test remains at a low level, the Breusch-Pagan test still have a decent amount of chance of rejecting the null hypothesis.

The power of visual test arises steadily as $log_e(E)$ increases from 2 to 5 in both non-linearity model and heteroskedasticity model, suggesting that the effect starts to make significant impact on the degree of the presence of the designed visual features. This can also be observed from the example residuals plots that when $log_e(E) = 2.5$, a weak "S-shape" and a weak "triangle" shape are presented in Figure \ref{fig:polypower} and Figure \ref{fig:heterpower} respectively. And as $log_e(E)$ increases, the visual pattern becomes much clearer, and the power reaches almost 100% at $log_e(E) \approx 6$.

The power of all inappropriate tests except for F-test shows improvement as the effect increases but at a lower rate than the visual test in both scenarios. This coincides the point made by @cook1982residuals that residual-based tests for a specific type of model defect may be sensitive to other types of model defects. The power curve of F-test remains at around 5% in Figure \ref{fig:heterpower} since there is no non-linear term leave out in the heteroskedasticity model and 
the null hypothesis of the F-test will be always satisfied.

@@

set.seed(10089)
ex_dat <- heter_model(a = 1, x = rand_uniform(-1, 1), b = 1)$gen(n = 100)
plist <- list()
j <- 0

### 2022-11-29 paper_comparison/paper_comparison/paper_comparison.tex
update power cmp

Figure \ref{fig:polypower} shows the estimated power of visual test on
lineups produced by the non-linearity model with the \(X_{raw}\)
following a uniform distribution against the natural logarithm of the
effect \(log_e(E)\) with comparison to the power of an exact test -
F-test, and two other residual-based conventional tests commonly used in
regression diagnostics but for testing heteroskedasticity and
non-normality respectively. At the bottom of the figure
\ref{fig:polypower}, there are a sequence of example residuals plots
with increasing levels of \(log_e(E)\). Readers can evaluate them from
left to right and determine at which level the departure from a good
residual plot becomes detectable.

In overall, the power of all four tests increases as the effect gets
larger. The power curve of F-test climbs aggressively from 25\% to
around 90\% as \(log_e(E)\) increases from 0 to 2, while power of other
tests respond inactively to the change of effect and remain lower than
25\% throughout the period, showing that F-test is way more sensitive to
the type of model defects that being considered. Meanwhile, no
noticeable visual features can be spotted from the example residuals
plots.

The power of visual test arises steadily to around 90\% as \(log_e(E)\)
increases from 2 to 5, suggesting that the effect starts to make
significant impact on the degree of the presence of the designed visual
features. This can also be observed from the example residuals plots
that when \(log_e(E) = 2.5\), a weak ``S-shape'' starts to present. And
as \(log_e(E)\) increases, the visual pattern becomes much clearer.
Other two inappropriate conventional tests shows improvement at the same
time but at a lower rate. This coincides the point made by
\citet{cook1982residuals} that residual-based tests for a specific type
of model defect are sensitive to other types of model defects.

At \(log_e(E) \approx 6\), the power of both F-test and visual test
reaches almost 100\%. The power of Breusch--Pagan test and Shapiro--Wilk
test reach around 75\% and 30\% respectively.

Similarly, Figure \ref{fig:heterpower} shows the power of BP test,
visual test and two other

>>>>

Figure \ref{fig:polypower} show the estimated power of visual test on
lineups produced by the non-linearity model with the \(X_{raw}\)
following a uniform distribution, against the natural logarithm of the
effect \(log_e(E)\) with comparison to the power of an exact test -
F-test, and two other residual-based conventional tests commonly used in
regression diagnostics but for testing heteroskedasticity and
non-normality respectively. At the bottom of the figure
\ref{fig:polypower}, there are a sequence of example residuals plots
with increasing levels of \(log_e(E)\). Readers can evaluate them from
left to right and determine at which level the departure from a good
residual plot becomes detectable.

Figure \ref{fig:heterpower} is similar to Figure \ref{fig:polypower},
but shows corresponding information on lineups produced by the
heteroskedasticity model. In this scenario, the visual test is compared
to an approximate test - Breusch-Pagan test, and two other inappropriate
tests - F-test and Shapiro-Wilk test.

For the non-linearity model, the power of all four tests increases as
the effect gets larger. The power curve of F-test climbs aggressively
from 25\% to around 90\% as \(log_e(E)\) increases from 0 to 2, while
power of other tests respond inactively to the change of effect and
remain lower than 25\% throughout the period, showing that F-test is way
more sensitive to the type of model defects that being considered.
Meanwhile, no noticeable visual features can be spotted from the example
residuals plots.

In terms of the heteroskedasticity model, the power of Breusch-Pagan
test is also almost always greater than the power of visual test. For
\(0 \leq log_e(E) \leq 2\), where the visual feature is nearly
unobservable from the example residual plots and the power curve of the
visual test remains at a low level, the Breusch-Pagan test still have a
decent amount of chance of rejecting the null hypothesis.

The power of visual test arises steadily as \(log_e(E)\) increases from
2 to 5 in both non-linearity model and heteroskedasticity model,
suggesting that the effect starts to make significant impact on the
degree of the presence of the designed visual features. This can also be
observed from the example residuals plots that when \(log_e(E) = 2.5\),
a weak ``S-shape'' and a weak ``triangle'' shape are presented in Figure
\ref{fig:polypower} and Figure \ref{fig:heterpower} respectively. And as
\(log_e(E)\) increases, the visual pattern becomes much clearer, and the
power reaches almost 100\% at \(log_e(E) \approx 6\).

The power of all inappropriate tests except for F-test shows improvement
as the effect increases but at a lower rate than the visual test in both
scenarios. This coincides the point made by \citet{cook1982residuals}
that residual-based tests for a specific type of model defect may be
sensitive to other types of model defects. The power curve of F-test
remains at around 5\% in Figure \ref{fig:heterpower} since there is no
non-linear term leave out in the heteroskedasticity model and the null
hypothesis of the F-test will be always satisfied.
